---
title: "troubleshooting.rmd"
author: "Eve Chen"
date: "2021/9/21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Welcome to R and Rmd!

This document is written in **R Markdown**. We'll use this document to explore the `mtcars` dataset.

First, let's store the current date as a variable. We can use the function `Sys.Date` with no arguments to get the current date:

```{r, error = TRUE}
## ERROR 1 ##
_today_ <- Sys.Date()
```

You may notice that, although an error might appear in these cells, this Rmd file knits just fine. That's because the `error = TRUE` _chunk option_ is included in each chunk, allowing the Rmd file to knit, even when an error is encountered.

Now, let's load the `tidyverse` (meta-) package:

```{r, error = TRUE}
## ERROR 2 ##
libraries(tidyverse)
```

By loading the tidyverse, a function called `glimpse` has been made available. This function is useful for viewing a data set. Let's take a look at the `mtcars` dataset by applying the `glimpse` function to `mtcars`!

```{r, error = TRUE}
## ERROR 3 ##
glimpse mtcars
```